Gradual Soundness: Lessons from Static Python

### 2022-02-03 pj-7.1/paper.tex
pj: ie -> eg
draft header

\titlerunning{DRAFT do not distribute}

@@

\authorrunning{DRAFT do not distribute}

@@

\Cref{t:microbenchmark} does not analyze benchmark configurations that mix
typed and untyped code. %% ---only fully-typed and untyped configurations.
A study of mixed configurations (i.e.,~\cite{gm-pepm-2018,gtnffvf-jfp-2019})
may reveal performance bugs that have not yet shown up in production.

>>>>

@@

\titlerunning{Draft document---please do not distribute or cite!}
\authorrunning{Draft document---please do not distribute or cite!}

@@

\Cref{t:microbenchmark} does not analyze benchmark configurations that mix
typed and untyped code. %% ---only fully-typed and untyped configurations.
A study of mixed configurations (e.g.,~\cite{gm-pepm-2018,gtnffvf-jfp-2019})
may reveal performance bugs that have not yet shown up in production.
